\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{fontawesome}

% Customizing section headings
\titleformat{\section}{
    \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-5pt}]

% Formatting hyperlinks
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

% Customizing the header
\pagestyle{fancy}
\fancyhf{}
\lhead{\textit{Dikshith Vishnuvardhan}}
\rhead{\thepage}

\renewcommand{\headrulewidth}{0pt}

\begin{document}

%==================== HEADER ====================
\noindent
\textbf{\LARGE Dikshith Vishnuvardhan}\\
\noindent
\faMapMarker \, Worcester, MA \quad
\faPhone \, (508)-615-3786 \quad
\faEnvelope \, \href{mailto:dvishnuvardhan@clarku.edu}{dvishnuvardhan@clarku.edu} \quad
\faLinkedinSquare \, \href{https://linkedin.com/in/dikshith-vishnuvardhan}{linkedin.com/in/dikshith-vishnuvardhan}

\vspace{-10pt}
\noindent\rule{\textwidth}{0.5pt}

%==================== SUMMARY ====================
\section*{Professional Summary}
Innovative and detail-oriented \textbf{Web Designer \& Developer} with over 4 years of experience designing and developing responsive web applications. Skilled in \textbf{ReactJS, Tailwind CSS, NodeJS, and REST APIs}, with expertise in component-based architecture, cloud deployments, and testing frameworks. Adept at delivering scalable, secure, and user-friendly solutions.

%==================== TECHNICAL SKILLS ====================
\section*{Technical Skills}
\noindent
\textbf{Languages \& Frameworks:} ReactJS, NodeJS, ExpressJS, JavaScript, TypeScript, HTML5, CSS, Tailwind CSS\\
\textbf{Tools \& Platforms:} Docker, AWS, GCP, Azure, Git, Bitbucket, WordPress\\
\textbf{Databases:} MySQL, MongoDB, PostgreSQL\\
\textbf{Other:} REST APIs, Microservices, Unit Testing, CI/CD Pipelines

%==================== EXPERIENCE ====================
\section*{Professional Experience}

\textbf{Software Development Engineer} \hfill \textit{September 2024 -- Present}\\
\textit{Trendline Labs, Atlanta, GA (Remote)}  
\begin{itemize}[leftmargin=*]
    \item Designed and developed \textbf{component-based architectures} for full-stack applications using \textbf{ReactJS, NodeJS}, and \textbf{ExpressJS}.
    \item Implemented responsive UI designs with \textbf{Tailwind CSS}, ensuring usability and scalability across devices.
    \item Built and integrated REST APIs, enhancing system performance and scalability.
    \item Deployed scalable solutions on \textbf{Google Cloud Platform (GCP)} with CI/CD pipelines, achieving minimal downtime.
    \item Achieved rapid growth with \textbf{450+ paying users} and 250 daily active users within 4 weeks post-launch.
\end{itemize}

\textbf{Research Assistant} \hfill \textit{December 2023 -- Present}\\
\textit{Clark University, Department of Mathematics and Computer Science, Worcester, MA}  
\begin{itemize}[leftmargin=*]
    \item Developed a scalable \textbf{video recommendation system} integrating \textbf{NextJS}, \textbf{Tailwind CSS}, and \textbf{NodeJS}.
    \item Integrated TikTok APIs and OpenAI models to deliver \textbf{personalized recommendations}.
    \item Deployed the system on \textbf{Azure} using \textbf{Docker}, ensuring scalability and security.
    \item Implemented client-side tracking to analyze engagement metrics, contributing to data-driven insights.
\end{itemize}

\textbf{Web Designer \& Data Analyst} \hfill \textit{February 2024 -- Present}\\
\textit{Clark University Career Connections Center, Worcester, MA}  
\begin{itemize}[leftmargin=*]
    \item Designed and built applications using \textbf{NodeJS, ReactJS}, and \textbf{Canva APIs}, streamlining event workflows by \textbf{75\%}.
    \item Managed the \textbf{WordPress Event Calendar} for CMS, optimizing scheduling and publishing processes.
    \item Analyzed unstructured survey data using \textbf{MySQL} and \textbf{Excel} to produce actionable reports.
\end{itemize}

\textbf{Software Development Engineer} \hfill \textit{December 2022 -- July 2023}\\
\textit{OpeninApp, Karnataka, India}  
\begin{itemize}[leftmargin=*]
    \item Led the frontend development for applications with \textbf{250,000+ daily active users}, achieving a \textbf{95 Lighthouse performance score}.
    \item Designed reusable components following \textbf{component-based architecture} principles.
    \item Reduced API response times by \textbf{50\%} through collaboration with backend teams.
    \item Implemented \textbf{WebSockets} for real-time communication and comprehensive testing protocols.
\end{itemize}

%==================== EDUCATION ====================
\section*{Education}
\textbf{Master of Science in Information Technology (STEM)} \hfill \textit{May 2025}\\
\textit{Clark University, Worcester, MA} \\
Overall: \textbf{3.9 GPA}

\textbf{Bachelor of Technology in Computer Science \& Technology} \hfill \textit{May 2022}\\
\textit{Dayananda Sagar University, Bangalore, India} \\
Overall: \textbf{3.0 GPA}

%==================== PROJECTS ====================
\section*{Projects}
\textbf{Personalized Video Recommendation System}  
Developed and deployed a scalable video recommendation platform integrating \textbf{NextJS}, \textbf{Tailwind CSS}, and \textbf{NodeJS}, leveraging TikTok APIs and OpenAI models. Deployed using \textbf{Azure} and \textbf{Docker} for secure, scalable operation.

\textbf{Chrome Extension -- Smart Link Generator}  
Built a browser extension with \textbf{ReactJS}, \textbf{NodeJS}, and \textbf{MySQL} to bookmark and analyze links, enabling real-time performance metrics and analytics.

%==================== FOOTER ====================
\vfill
\noindent\rule{\textwidth}{0.5pt}\\
\footnotesize{\textbf{Dikshith Vishnuvardhan} | \href{mailto:dvishnuvardhan@clarku.edu}{dvishnuvardhan@clarku.edu} | (508)-615-3786 | \href{https://linkedin.com/in/dikshith-vishnuvardhan}{linkedin.com/in/dikshith-vishnuvardhan}}
\end{document}
